\chapter*{参考文献\markboth{参考文献}{参考文献}}
\addcontentsline{toc}{chapter}{参考文献}
\fontsize{10.5pt}{16pt}\selectfont
\addtolength{\itemsep}{-.1 em} % 缩小同一参考文献条目内的行间距
%******************************************************************
\begin{thebibliography}{990}
%====== ch = intro ========
\bibitem{kim2007} Kim, K.
      Chapter 1: Overview of electronic and algorithmic trading,
      Electronic and algorithmic trading technology: the complete guide[M],
      Academic Press(Elsevier Inc.): United Kingdom, 2007.6.

%====== ch2 行为预期 ========
\bibitem{shleifer1997} Shleifer, A., and Vishny, R.
      The limits of arbitrage, Journal of Finance, 1997(52):35-55.
\bibitem{shiller1984} Shiller, R.
      Stock prices and social dynamics,
      Brooking Papers on Economic Activity, 1984(2):457-498.
\bibitem{zhao2007}Montier, J.(著), 赵英军(译).
      行为金融：洞察非理性心理和市场[M], 北京:中国人民大学出版社, 2007.
\bibitem{tang2005}唐寿宁, 投资经济学的立宪理论[M],北京:人民大学出版社, 2005.

%====== ch2 规则预期 ========
\bibitem{leigh2008}Leigh, W., Frohlich, C.J., and Hornik, S.\emph{et. al.},
   Trading with a stock chart heuristic[J],
   IEEE Trans. on Systems, MAN, and Cybernetics,
   2008, 1(38):93-104.


%====== ch2 市场中性策略 ========
\bibitem{yang2004}杨晓光\, 张静\, 刘希民.
      市场中性策略简介[J], 管理评论, 2004, 9(16):25-28.

%====== ch = measu ========
\bibitem{joe1996} Joe, H. and Xu, J.J.
      The estimation method of Inference Functions for Margins for Multivariate Models,
      Tech. Rept.-166, 1996, Dept. of Statistics, University of British Columbia.
\bibitem{song2005} Song, P., Fan, Y. and Kalbfleisch, J.
      Maximization by Parts in Likelihood Inference,
      Journal of the American Statistical Association, 2005, 100: 1145-1158.

%----------CH 2 sec : pair-copula---------------
\bibitem{embrechts2003} Embrechts, F., Lindskog, F. and McNeil, A.
      Modeling dependence with copulas and applications to risk management[M],
      Elsevier, North-Holland, 2003.
\bibitem{whelan2004} Whelan, N.
      Sampling from archimedean copulas[J],
      Quantitative Finance, 2004(4):339-352.
\bibitem{mcneil2008} McNeil, A.
      Sampling from nested archimedean copulas[J],
      Journal of Statistical Computation and Simulation, 2008(6):567-581.
\bibitem{bedford2002} Bedford, T. and Cooke, RM.
      Vines --- a new graphical model for dependent random variables[J],
      Annals of Statistics, 2003(30):1031-1068.


%====== ch6: pair trading=======
\bibitem{engle1987} Engle, R. and Granger, C.
      Co-integration and error correction: representation, estimation, and testing,
      Econometrica, 1987, 55(2):251-276.
\bibitem{vidy2004}Vidyamurthy, G.
      Pairs trading, Quantitative methods and analysis[M], 2004, John Whiley\&Sons, Canada.

%========Appendix B: statComp======
\bibitem{mariano2000} Mariano, R., Schuermann, T., and Week, M.J.
      Simulation-based inference in econometrics[M],
      England Cambridge:Cambridge University Press, 2000.
\end{thebibliography}
